\section{Exercise 4}
Three systems will be compared, namely the Coronapas App, Git, and a Insulin pump control system.

\subsection{Dependability}
% Coronapas App
If the Coronapas App were to go down or fail it would cause some economic damage, to shops and buisnisses that rely on the app.
There are other ways of validating ones Coronapas, and as such it would mostly be an inconvenience for the end user. 
Dependability is of import, but not critical.

% Git
Loosing acess to git would make it impossible to track changes to sourcecode.
Existing code would not dissapear, and development could still occour during the downtime.
Hence, a short time failure or breakdown, would not be problematic but a permanent loss would be.
Therefore, short term dependability is not that important for git.


% Insulin pump control system
Failure of the Insulin pump control system can be categorised in two broad groups.
It can either give too much, or too little insulin.
Both types of failure will cause physical damage to the end user, both on the long and short term.
Hence it is really importat that the controll system does not fail, and is dependable.

% Software dependability includes a range of characteristics including reliability, security, and safety. 
% Dependable software should not cause physical or economic damage in the event of system failure. 

\subsection{Security}
Clearly all of the systems need to be secure.
For the Coronapas App, missing secutity could allow malicious actors to get hold of peoples health data, or allow a malicious actor to have a fake clearence.
This would be problematic for the customer, the danish government.
For git, it could cause publication or changes to code repos, or other files tracked via it.
The Insulin pump control system, too needs to be kept secure from outside interferance.
Not doing so could cause the system to deliver too much insulin to the end user, killing them.
As such, this system is safety-critical

% Sometimes security for embeded systems, and systems that are not connected to othes, is not prioritized.
% This could be the case for the Insulin pump control system, with the argument that there are no obvious attack vectors.
% Hence the business of The Insulin pump control system might not put an emphasis on security.
% This is a hyphothetical, because this system is safety-critical.


\subsection{Efficiency}
It is important that all three systems operate efficiently, and use as few resources and as little time as possible.

% Coronapas App
The Coronapas App is often run of phones, that have a lot of resources available, and is only used for a short while for each use.
So efficiency is less of a consern to the buisniss, since even if it hogs resources, they will be released quickly.


%Git
Git has a high requrements for efficiency, because of its usecase.
Since git was originally build to facilitate the development of the linux kernel, it would have a lot of users working on the same code repo.
As such many people would need to be kept in synchronization often.
Hence git needs to be fast to avoid waittimes, for its users.

% Insulin pump control system
In order to make the Insulin pump control system affordable, it needs to be as simple and cheap as possible.
Cheaper hardware often has fewer resources to work with.
Hence it needs to be efficient with the resources it has.
On the other hand, insulin is not a time sentitive drug in the order of seconds.
That is to say, it does not matter if the control system takes, $10^{-9}$ or $10^{-7}$ seconds to calculate something.
It matters that pump is controlled, not how fast.

% Software should not make wasteful use of system resources such as memory and processor cycles. 
% Efficiency therefore includes responsiveness, processing time, resource utilization, etc.


\subsection{Maintainability}
Maintainability is only relevant, if there are changing needs of customers.
For the Coronapas App, it was a shortlived, approximately 2 years, and had a defined set of requrements from the beginning.
Hence, there was not a significant need for maintainability within the app.

Similarly, the Insulin pump control system does not have not a significant need for maintainability.
That is, once the pump works and operates correctly, the needs of customers should not change too much.
It is not that there will be no changes to the requremnts, but they will be few and far between.

Contrary to those examples, git often has changes to its needs.
The source code repo for git has over 67000 commits, and as such it gets changed really often.
In principal, there does not need to be a change to the needs of git's customers, but there are.
Hence gits business or devs has placed a high prioriry on maintainability


% Sommerville discusses quality of professional software, non-functional quality attributes, or product characteristics. 
% Compare the Coronapas App, Git, and the Insulin pump control system (see SE chap 1.3.1) with respect to the quality attributes dependability, security, efficiency, and maintainability.

% Do they all share the same characteristics with regards to these quality attributes or are these of varying importance to the three systems? 
% Give examples for each of the three systems with regards to each of the quality attributes above.

% Book refrence: p. 24, p. 34